\documentclass[12pt]{article}
\special{papersize=3in,5in}

\usepackage{amssymb,amsmath}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\providecommand{\st}{\ \text{s.t.}\ }
\providecommand{\tightlist}{
    \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}
}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  mathescape
}


\pagestyle{empty}
\setlength{\parindent}{0in}
\begin{document}

\section{GREEDY ALGORITHMS}
\subsection{Max Num Non-Overlapping Intervals pt 1}
\begin{itemize}\tightlist
  \item Exchange at the interval where Opt(I) and A(I) first disagree.
  \item Then Opt'(I) doesn't overlap on the left, since they agree to that point.
  \item Nor on the right, since the A(I) interval ends first.
  \item Opt'(I) has just as many intervals, so still optimal.
\end{itemize}


\subsection{Max Num Non-overlapping Intervals pt 2}
A = pick the interval that overlaps the least number of other intervals\\
(this is wrong, see pic for counterexample)


\subsection{Earliest Deadline First}
EDF = pick as the next job the one whose deadline is earliest
\begin{itemize}\tightlist
  \item At some point Opt runs job $j$ and EDF runs job $i$.
  \item Opt' = Opt except running $i$ at that point.
  \item 3 things:
  \item \begin{itemize}\tightlist
    \item Length of time (obviously fine)
    \item Release time -- EDF ran $i$ at that time (so fine)
    \item Deadlines -- $j$ is not past deadline in Opt' since (by EDF) $i$ ends first, and (by Opt) that is at least 1 unit after when Opt runs $i$
  \end{itemize}
\end{itemize}


\subsection{Kruskal's (MST)}



\subsection{Huffman's Algorithm}
Given input set of numbers, build a tree to minimize $sum(depth * weight)$\\
\begin{itemize}\tightlist
  \item First point of disagreement is some pair of neighbors $A$ and $B$ in H(I), where in Opt(I) $A$ is with $X$ and $B$ is with $Y$ (all subtrees).
  \item Opt' = Opt but switch $Y$ and $A$. It is more similar ($X$ and $Y$ haven't already paired in H(I), being of greater weight)
  \item $\Delta(Objective) = (+A*h) - (Y*h) \leq 0 \iff A \leq Y$
  \item Consider state of H when pairing $A$ and $B$: Opt $\rightarrow$ Opt' $\Delta(Objective) \leq 0$ $\implies$ just as optimal
\end{itemize}


\subsection{Interval Coloring Problem, pt 1}
Find an assignment of classes to rooms that uses the fewest number of rooms.\\
A = Assign as many as possible to 1st room (via the 'smallest rightpoint first' algorithm), then as many as possible to 2nd room, etc.


\subsection{Interval Coloring Problem, pt 2}
Find an assignment of classes to rooms that uses the fewest number of rooms.\\
Process in increasing order of start times. Take class $C$. If $\exists$ room $R$ \st $C$ can be assigned to $R$ without overlapping previously assigned classes, then assign $C$ to $R$. Otherwise, put $C$ in a new room.
\begin{itemize}\tightlist
  \item Lemma: In any collection of intervals, there exist points which have the maximum number of intervals, say $n$, intersecting at the same time. This means that there is no way to fit these classes with any fewer than n rooms.
  \item Now consider a course. Each room is chosen by start time, so all previous rooms are already placed.
	This course overlaps with some ($n$) already placed, and some ($m$) not yet placed.
	\item Placing this course will require $n+1$ rooms to be optimal, by the lemma above.
	\item Now, because the other n have been placed, this course conflicts with them all, and thus requires exactly $n+1$ rooms. This process repeats for each course.
\end{itemize}


\subsection{Gas Station pt 1}
Minimize time stopped for gas.\\
A = stop at each station and fill just enough to get to the next station.
\begin{itemize}
  \item At some point Opt must fill more than A does.
  \item In Opt', fill the same as A at this point, and fill the extra at the next stop.
  \item Opt' has the same total fuel as Opt and is more similar to A.
\end{itemize}

\subsection{Gas Station pt 2}
Minimize time stopped for gas.\\
A =  Stop iff you don't have enough gas to make it to the next station; if you stop fill up all the way.\\
This is wrong. Consider $x_1 = 0, x_2 = 5, x_3 = 6$, with a gas tank that lasts 5km. Then you have extra fuel at the end compared to the other algorithm (FAYG).

\subsection{Placing Words on Lines pt 1}
Minimize total penalty.\\
A = Place the next word on the current line if it fits, else place on a new line.
\begin{itemize}
  \item Opt must put a word $w_i$ that would have fit on line $l$ onto $l+1$.
  \item Opt' has $w_i$ on $l$, and the penalty on $l+1$ has increased by at most $|w_i|$.
\end{itemize}

\subsection{Placing Words on Lines pt 2}
Minimize max line penalty.\\
A = Place the next word on the current line if it fits, else place on a new line.
\begin{itemize}
  \item Let $L = 5$, and our input be words of the following length $(2,3,1)$.
\end{itemize}
\begin{center}
\begin{tabular}{l | l}
  A(I) & Opt(I)\\
  \hline
  5-(2+3)=0 & 5-2 = 3\\
  5-1=4     & 5-(3+1)=1\\
\end{tabular}
\end{center}


\subsection{Skiers and Skis pt 1}
Minimize total difference between heights of skiers and skis.\\
\begin{verbatim}
Repeat this process until every skier has a ski:
    Find the skier and ski whose height difference is minimized.
    Assign the skier this ski.
\end{verbatim}
Consider skis = (4,8) and people = (7,12)


\subsection{Skiers and Skis pt 2}
Minimize total difference between heights of skiers and skis.\\
\begin{verbatim}
Sort the people and skies in order of increasing height.
Assign to each person the ski in the same position in the ordering.
\end{verbatim}
 \begin{itemize}
  \item Persons and skis are ordered. In Opt the skis are swapped for some person $i$ and some person $m$. Then we show Opt is no better than Opt'. 4 elements to order, 6 cases (absolute value).
\end{itemize}


\subsection{Job Scheduling pt 1}
Schedule a job-unit at each time $t$ to minimize total completion time.\\
A = Pick $J_m$ to be the job with minimal size $x_i$.
(Counterexample)

\subsection{Job Scheduling pt 2}
Schedule a job-unit at each time $t$ to minimize total completion time.\\
A = Pick $J_m$ to be a job which has minimal remaining processing time.
\begin{itemize}\tightlist
  \item A runs job $i$ at time $t$, Opt runs job $j$.
  \item T = \{time slots after $t$ where $i$ or $j$ is run in Opt\}
  \item Opt' = Opt but run $i$ through then $j$ (during T)
  \item Since $i$ has no more remaining time than $j$, running shorter first is optimal for two jobs.
\end{itemize}


\subsection{Page Replacement}
Do 'Not Used in the Future' (NUF).



Other Greedy:
\begin{itemize}
  \item 1 max cardinality non-overlapping intervals   x
  \item 2 interval coloring                           x
  \item 4 gas station                                 x
          FAYG vs. Fill all the way
  \item 6 words and line length                       x
  \item 7 Make your own page replacement              x
          (Not Used in the Future)
  \item 9 skiers and skis                             x
          Minimize difference vs. shortest w/ shortest ... tallest w/ tallest
  \item 10 SJF and SRPT                               x
  \item 12 Matrix of 1's and 0's
  \item 13 Jobs w/ machine, release time, deadline
  \item 16 Torch and Bridge (hard)
  \item 17 Husband and wife
\end{itemize}


\pagebreak

Now DP:


\subsection{Fibonacci}
Write a DP alg to calculate the $n^{th}$ Fibonacci number.\\
\begin{verbatim}
Fib[0] = Fib [1] = 1
for i=2 to n
  Fib[i] = Fib[i-1] + Fib[i-2]
\end{verbatim}

\subsection{Max Value Independent Set}
\begin{itemize}\tightlist
  \item For any considered node x need to know whether children (y and z) are in the set or not.
  \item Profit[x] = max profit (overall) from subtree rooted at x
  \item ProfitNR[x] = max profit from subtree rooted at x that excludes x
\end{itemize}
\begin{verbatim}
Start anywhere then recurse on subtrees:
  ProfitNR[x] = Profit[y] + Profit[z]
  Profit[x] = max{ProfitNR[x], ProfitNR[y] + ProfitNR[z] + Px}
\end{verbatim}


\subsection{MinWeight BST}
Given keys $K_i$ with weights $w_i$, output BST that minimizes $sum_{i=1}^n w_i * (depth at K_i)$\\
\begin{itemize}
  \item Bottom-right to top-left
  \item $$MWBST[l][r] = min_{l\leq c\leq r}\{MWBST[l][c-1] + MWBST[c+1][r]\} + \sum_{i=l}^r w_i$$
  \item Diag = base case = $w_i$
  \item Over each possible root $c$, split into the two subtrees
\end{itemize}



\subsection{LIS}
Input: sequence of numbers; Output: LIS\\
\begin{itemize}
  \item Naive recursion doesn't give enough info
  \item LIS[i][k] = smallest last num of incr. subsequence of first i nums of length k
\end{itemize}
\begin{verbatim}
for i = 1 to n
  for k = 1 to i
    if x[i] < LIS[i-1][k-1]
      LIS[i][k] = LIS[i-1][k]
    else
      LIS[i][k] = min{LIS[i-1][k], x[i]}
return max{LIS[n][all]} s.t. it is defined
\end{verbatim}


\subsection{Subset Sum (change-making)}
Input: positive ints (coin values)\\
Output: 1 if $\exists$ subset that sums to L, otherwise 0\\
\begin{itemize}
  \item Prune subtrees with sum > L
  \item If 2 nodes w/ same sum on same level, prune \textbf{either one}
  \item Index by level, then sum $\rightarrow$ A[k][s] = 1 $\iff \exists$ a subset from $x_1 - x_k$ w/sum = s
\end{itemize}
\begin{lstlisting}
for k=0 to n-1
  for s=0 to L
    if A[k][s] = 1
      A[k+1][s] = 1  //left child
      A[k+1][s + $x_{k+1}$] = 1   //right child
\end{lstlisting}


\subsection{Knapsack}
Input: Pos. weights $w_i$ w/ values $v_i$, and weight limit L\\
Output: Max \textbf{value} from a subset w/ weight $\leq$ L\\
\begin{itemize}
  \item If total weight $>$ L then prune
  \item If $\exists$ two nodes @ same level with same weight, prune lower value
  \item A[i][w] = max val of subset of first i elements of total weight w
\end{itemize}
\begin{lstlisting}
for i=0 to n
  for w=0 to L
    if A[i][w] defined
      A[i+1][w] max= A[i][w]    //left child
      A[i+1][w+$w_{i+1}$] max= A[i][w] + $v_{i+1}$  //right child
output max{A[n][all]} s.t. it is defined
\end{lstlisting}


\subsection{LIS (method 2)}
Input: sequence of numbers; Output: LIS\\
\begin{itemize}
  \item Prune nonincreasing subsequences
  \item If 2 subsequences @ same level end on \textbf{same last num}, prune shorter
  \item A[i][k] = length of longest inc. subsequence of $x_1 \dots x_i$ that ends in $x_k$
\end{itemize}
\begin{lstlisting}
for i=1 to n    //levels
  for k=1 to i  //possible endings
    if A[i-1][k] is defined
      A[i][k] max= A[i-1][k]    //left child
      if $x_i > x_k$
        A[i][i] max= A[i-1][k] + 1    //right child
output max{A[n][all]}
\end{lstlisting}







\subsection{Chapters into Volumes}
Input: Number of pages in each of $n$ chapters $x_1 \dots x_n$ and desired \# volumes $k$\\
Output: Which chapters go in each vol to minimize difference between max/min pages in any volumes
\begin{itemize}\tightlist
  \item Let A[i][j][p][q] denote the optimal method (store a solution, not a simple value, in every cell) to divide the first j chapters into i volumes, w/ vol of the largest \# of pages starts from chapter p and ends at chapter q.
  \item For each cell you have, you may write two other cells: putting a new chapter in the last volumn, or putting a new chapter in a new volumn.
  \item In the end, find the best solution in matrix A[k][n], which will be the output.
\end{itemize}

\subsection{Pan Balance}
Input: Set of boxes $B_1, \dots, B_n$ and pan balance (and $\exists$ max boxweight L)\\
Output: Determine if you can partition them into two sets of equal weight\\
\begin{itemize}\tightlist
  \item If any subcollection outweighs what is left (using balance) delete that node
  \item If two nodes @ same level have equal weight (using balance) prune one
  \item Now at most $\dfrac{1}{2}nL$ nodes in each level (max sum is $nL$)
  \item Tricky part is second pruning rule (see code): use two working queues, with $Q(i)$ = ordered queue by weight of all subcollections in level $i$, then: 1) put every $C \cup \{B_i\}$ from FirstQ into SecondQ if less than half (check for equality/solution), this orders FirstQ and SecondQ by weight; 2) merge two queues and get rid of queues of equal weight, which creates $Q(i)$ as an ordered queue
\end{itemize}
\begin{lstlisting}
Test $B_1$ and $B_1^C$, if $>$ then return False (or $=$ return True)

Q(1) = $\{B_1\}$
for i=2 to n
  FirstQ = Q(i-1)
  SecondQ = ()

  //Get elements from FirstQ from light to heavy
  for C = Dequeue(FirstQ)
    compare $C \cup \{B_i\}$ with its complement
    if $<$ then Enqueue(SecondQ,$C \cup \{B_i\}$)
    if $=$ then return True

  //now we should have FirstQ and SecondQ ordered by weight
  //merge them and get rid of duplicates
  $C_1$ = Dequeue(FirstQ)
  $C_2$ = Dequeue(SecondQ)
  while FirstQ not empty
    compare $C_1$ and $C_2$
    if $<$ then
      Enqueue(Q(i),$C_1$)
      $C_1$ = Dequeue(FirstQ)
    else if $>$ then
      Enqueue(Q(i),$C_2$)
      $C_2$ = Dequeue(SecondQ)
    else    //must be equal
    Enqueue(Q(i),$C_1$)
    $C_1$ = Dequeue(FirstQ)
    $C_2$ = Dequeue(SecondQ)

  //at this point Q(i) is ordered queue by weight of all subsets in level $i$

return False
\end{lstlisting}





\subsection{Requests and Broadcasts}
Input: Sequence $R_1 \dots R_n$ of requests at time $i$, and $k$ max broadcasts\\
Output: Optimal broadcast schedule to minimize total wait time
\begin{itemize}\tightlist
  \item A[i][j] = min total wait time from requests $R_1 \dots R_i$ and $j$ broadcasts
\end{itemize}
\begin{lstlisting}
for i=1 to n    // levels (num requests)
  for j=1 to k  // broadcasts (up to limit k)
    if j==1   // for single-broadcast must be at end, sum up all
      A[i][j] = 0
      for m=1 to i
        A[i][j] += $R_m$ * (i - (m - 1))
    else      // else calculate best broadcast time for subprob
      A[i][j] = $\infty$
      for b=j-1 to i
        temp = A[b][j-1]
        for m=b+1 to i  // sum wait time
          temp += $R_m$ * (i - (m - 1))
        if temp $<$ A[i][j]    // if this is better than what is there, reassign
          A[i][j] = temp
\end{lstlisting}



\subsection{Requests and Broadcasts, hard}
Input: Array $R$ of requests $R_{t,p}$ for page $p$ at time $t$, and $k$ max broadcasts\\
Output: Optimal broadcast schedule to minimize total wait time
\begin{itemize}
  \item Suppose $R$ is $n$ by $m$, so \# pages is $m < k$ and ending time is $n$
  \item Let $W(p,l_p)$ be min wait time for page $p$ with at most $l_p$ broadcasts of $p$ under requests $R_{1,p}, \dots, R_{n,p}$. We solved this subproblem in problem 23. Just need to assign each $l_i$.
  \item Prune any assignment of $l_i,\dots,l_i$ with sum $> k$
  \item If two subsets at same depth $i$ with same sum, eliminate the one with higher total wait time
  \item Let $T(p,j)$ be min total wait time from $l_1 + \dots + l_p = j$ (with $p \leq j$)
\end{itemize}
\begin{lstlisting}
for p=1 to m
  for j=p to k
    T(p,j) = $\infty$
    for l=1 to j-(p-1)
      compute W(p,l) by calling prob 23 on page p
      if T(p,j) > T(p-1,j-l) + W(p,l)
        T(p,j) = T(p-1,j-1) + W(p,l)    // get min time
output T(n,k)
\end{lstlisting}


\subsection{Bahncards}
Input: Set of $n$ train trips, dates $d_i$ of each trip, regular fare $f_i$ of each trip, $L$ days of Bahncard bonus\\
Output: When to buy a Bahncard to minimize cost of travel
\begin{itemize}
  \item Order by date, then A[i][j] = min possible total cost of taking first $i$ trips when last Bahncard was purchased before trip $j$
\end{itemize}
\begin{lstlisting}
for i=1 to n
  A[i][0] = A[i-1][0] + $f_i$  //consider if no card is bought
  for j=1 to i
    if i==j  //buy card
      A[i][j] = $\infty$
      for k=0 to i
        if (A[i-1][k] + $f_i$) / 2 + CARD_COST < A[i][j]
          A[i][j] = (above)
    else if (i > j && $d_i - d_j < L$)  // check if card is still active
      A[i][j] = A[i-1][j] + $f_i$ / 2
    else    // use full fare
      A[i][j] = A[i-1][j] + $f_i$
\end{lstlisting}


\subsection{LCS}
Input: two or three strings A,B,C\\
Output: LCS
\begin{itemize}
  \item Recursive:
  \begin{lstlisting}
  if A[m] == B[n]
    return LCS(m-1,n-1) + 1
  else
    return max{
      LCS(m-1,n),   //take A[m]
      LCS(m,n-1)   //take B[n]
    }
  \end{lstlisting}
  \item Iterative:
  \begin{lstlisting}
  for i=1 to m
    for j=1 to n
      if X[i] == Y[j]
        LCS[i][j] = LCS[i-1][j-1]+1
      else
        LCS[i][j] = max{LCS[i-1][j], LCS[i][j-1]}
  return LCS[m][n]
  \end{lstlisting}
\end{itemize}



\subsection{Path Backtracker}
Input: n points on a line\\
Output: path P that covers every point and minimizes total response time
\begin{itemize}
  \item Number from left to right
  \item Tree where each level $l$ contains all solutions for visiting exactly $l$ points
  \item Prune two solns @ same level with same last visited point -- must have already visited same set -- keep one with min total resp time plus (n-l)*length of path
  \item Iterate over levels, then points -- Cost array and Length array [l,k] visits l points, ends at $p_k$, minimizes total time
\end{itemize}



\subsection{Cheapest String Conversion}
Given two strings A, B, begin at the final character of each.
If these characters agree, then move on to the next one.
If they don't, then try each of the following, and choose the option with lowest cost:
\begin{itemize}\tightlist
    \item Delete the current character from A, and continue on in A, keeping the same position in B.
    \item Insert the character from B into A, and continue on in B, keeping the same position in A.
    \item Replace the character from A with the one from B, and move onto the next character in each.
\end{itemize}
Recursive:
\begin{lstlisting}
function CSC(a, b):
if a == 0 then return 4b // Insert the rest of B
if b == 0 then return 3a // Delete the rest of A
if A[a] == B[b] then
    return CSC(a-1, b-1)
else
    return min(
        3 + CSC(a-1, b),  // Delete A[a]
        4 + CSC(a, b-1),  // Insert B[b]
        5 + CSC(a-1, b-1) // Replace A[a] <- B[b]
    )
\end{lstlisting}

Iterative:
\begin{lstlisting}
int CSC[n+1][m+1]
for b = 0 to m do
  CSC[0][b] = 3b
for a = 0 to n do
  CSC[a][0] = 4a

for a = 1 to n do
for b = 1 to m do
  if A[a] == B[b] then
    CSC[a][b] = CSC[a-1][b-1]
  else
    CSC[a][b] = min(
      3 + CSC[a-1][b],
      4 + CSC[a][b-1],
      5 + CSC[a-1][b-1]
      )

return CSC[n][m]
\end{lstlisting}



\subsection{Max Consec Sum}
\begin{itemize}\tightlist
  \item MCS(i) = Max Consecutive Sum of the first i ints
  \item MSS(i) = Max Consecutive Sum of first i ints that uses $x_i$
\end{itemize}
\begin{lstlisting}
for i=1 to n
  MSS[i] = max{0,MSS[i-1]+$x_i$}
  MCS[i] = max{MCS[i-1],MSS[i-1]+$x_i$}
\end{lstlisting}



\end{document}



\begin{centering}\textbf{Gas Station pt 1}\par\end{centering}
